%-------------------------
% Resume in Latex
% Author: Thilakkumar V
% Based off of: https://github.com/Thilak-07/LaTeX_resume
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage{fontawesome5}
\usepackage{xparse}

% ----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
\usepackage{charter}
% \usepackage{CormorantGaramond}
% \usepackage{lato}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\footskip}{4.08003pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1


%-----------Custom Commands----------------------------------------------------
% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\NewDocumentCommand{\resumeSubheading}{ m m m m o }{
    \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\textbf{\small#2}} \\
      \textit{\small#3} & \textit{\small#4} \\
      \IfValueT{#5}{\multicolumn{2}{l}{\textit{\small #5}}} % Include the fifth argument if provided
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textit{\textbf{\small#2}} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\achievement}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      {\small \textbullet\ #1} & \textit{\textbf{\small#2}} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%------------HEADING------------
\begin{center}
    \textbf{\Huge Thilakkumar V} \\ \vspace{2pt}
    {\raisebox{0.0\height}{\footnotesize \faPhone}\
    \footnotesize +91-9092776817} $|$
    \href{mailto:vinaythilak002@gmail.com}
    {\raisebox{-0.1\height}{\footnotesize \faEnvelope}\
    \footnotesize \underline{vinaythilak002@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/thilakkumar-v-65610a200/}
    {\raisebox{-0.1\height}{\footnotesize \faLinkedin}\
    \footnotesize \underline{linkedin.com/in/thilakkumar-v}} $|$
    \href{https://github.com/Thilak-07}
    {\raisebox{-0.1\height}{\footnotesize \faGithub}\
    \footnotesize \underline{github.com/Thilak-07}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National Institute of Technology, Tiruchirappalli}{2020 -- 2024}
      {Bachelor of Technology in Civil Engineering, Minors in Computer Science}{8.21 CGPA}
      [Relevant Coursework: Data Structures, DBMS, Artificial Intelligence, Operating Systems, Software Engineering]
    \vspace{-2pt}
    \resumeSubheading
      {Shree Niketan Matric. Hr Secondary School, Chennai}{2020}
      {Class XII, Central Board of Secondary Education}{91.17\%}
    % \vspace{-2pt}
    % \resumeSubheading
    %   {Vivekananda Vidyalaya, Chennai}{2018}
    %   {Class X, Central Board of Secondary Education}{95.20\%}
  \resumeSubHeadingListEnd \vspace{-5pt}


%-----------EXPERIENCE----------    
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {{Business Analyst Intern} $|$ {BlockTrack}}{May 2023 -- Jul 2023}
      {An IIT Madras incubated Health-tech startup specializing in Blockchain and SaaS products}{Chennai, TN}
      \resumeItemListStart
        \resumeItem{Conducted competitive analysis of \textbf{50+ rivals}, identifying trends and fostering collaboration.}
        \resumeItem{Applied \textbf{PEST analysis} to refine market positioning, boosting \textbf{profit margins by 5\%} and \textbf{market share by 15\%}.}
        \resumeItem{Designed advanced insurance modules, enhancing functionality and targeting a \textbf{75\% increase in customer base}.}
        \resumeItem{Analyzed \textbf{2000+ stakeholder surveys}, deriving insights that informed \textbf{6 strategic action plans}.}
      \resumeItemListEnd
    % \vspace{-2pt}
  \resumeSubHeadingListEnd


%-----------PROJECTS------------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Predictive Drought Risk Model} $|$ \emph{Python, ArcGIS, MLR, SVM, Looker Studio}}{Jan 2024 -- May 2024}
          \resumeItemListStart
            \resumeItem{Integrated historical data \& EC-Earth3 projections under CMIP6 framework, covering 6500+ rain gauge stations.}
            \resumeItem{Enhanced predictive \textbf{accuracy by 20\%} with advanced bias correction techniques (MLR, SVM)}
            \resumeItem{Automated 7.5 lakh SPI iterations to quantify drought characteristics in the Cauvery River Basin.}
            \resumeItem{Designed interactive dashboards and spatial visualizations using \textbf{Google Earth Engine} for actionable insights.}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{YouTube Revenue Forecast System} $|$ \emph{Machine Learning, Pandas, Scikit-learn, SQL, Folium}}{Oct 2023 -- Dec 2023}
          \resumeItemListStart
            \resumeItem{\textbf{Executed Data Cleaning:} Addressed outliers, null values, and empty records to ensure robust dataset quality.}
            \resumeItem{\textbf{Conducted Exploratory Data Analysis (EDA):} Created choropleth maps and informative bar charts to reveal subscriber concentrations, regional trends, and niche opportunities within channel categories.}
            \resumeItem{\textbf{Engineered Features:} Developed “Engagement Rate” feature and applied data scaling for model consistency.}
            \resumeItem{\textbf{Developed Predictive Models:} Applied hyperparameter tuning for model optimization, Achieved 93\% accuracy with Linear Regression, 100\% with Decision Tree, and 95\% with Random Forest for forecasting channel earnings.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small \item{
         \textbf{Languages:}{ Python, SQL (MySQL), C/C++, JavaScript} \\
         \textbf{Libraries:}{ Pandas, NumPy, Matplotlib, Seaborn, Scikit-Learn, TensorFlow} \\
         \textbf{Web Stack:}{ HTML/CSS, ReactJS, Node.js, Express.js, Tailwind, Bootstrap} \\
         \textbf{Tools:}{ PowerBI, Advanced Excel, Tableau, Looker Studio, Jupyter Notebook, MATLAB, VS Code, Google Cloud Platform} \\
         \textbf{Certifications:}{ Data Analysis and Visualization using Python, Excel and Cognos, Databases \& SQL for Data Science}
    } \vspace{-5pt}
 \end{itemize} \vspace{-5pt}


%-----------POSITIONS OF RESPONSIBILITY-----------
\section{Leadership / Activities}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Chairperson, Nittfest’23} $|$ \emph{The Annual Cultural Festival of NIT Trichy}}{Mar 2022 -- May 2024}
          \resumeItemListStart
            \resumeItem{Led and coordinated a \textbf{3-tier team} of \textbf{250+ members}, executing 80+ events for 12000+ students.}
            \resumeItem{Managed a \textbf{75 lakh INR }budget with strategic marketing, promotions, and risk management.}
            \resumeItem{Organized events featuring high-profile guests like \textbf{Dr. Kamal Haasan}, partnering with \textbf{7+ production houses}.}
            \resumeItem{Increased corporate \textbf{sponsorship by 70\%} through innovative branding and outreach for \textbf{50+ companies.}}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Consultant} $|$ \emph{180 Degrees Consulting, NIT Trichy}}{Aug 2022 -- May 2024}
          \resumeItemListStart
            \resumeItem{Handled 4 consulting projects (3 start-ups, 1 NGO), with an \textbf{NPS of 100\%} across clients.}
            \resumeItem{Within the \textbf{FinTech Innovation Project - BharatX}, conducted primary research on 10+ professional education loan systems, analyzed 5-year Indian Ed-Tech market growth with 7 parameters, and \textbf{devised 3 innovative strategies}.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


% -----------ACHIEVEMENTS-----------
\section{Achievements}
    \resumeSubHeadingListStart
        \achievement
        {\textbf{Secured 1st Position}, Smart India Hackathon, MHRD, Government of India}{May 2021}
        
        \achievement
        {\textbf{Github Arctic Code Vault Contributor}, Contributed code to several repositories}{May 2023}
    \resumeSubHeadingListEnd


%-----------CERTIFICATIONS------------------
%-------------------------------------------


\end{document}